Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-23 doc/JFLA2022/paper.tex
Add institution
Clarify legend of figure 1 (I think?)
Make hydra symmetric
Clarify what happens in figure 1

\usepackage{doc}
\usepackage{tikz}
\usepackage{tikzsymbols}
\newtheorem{theorem}{Theorem}
\usetikzlibrary{arrows}

@@

\institute{
Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France \\
  \email{pierre.casteran@labri.fr}
\and
to fill!
\and
to fill!
\and
to fill!
\and
to fill!
 }

@@

\begin{figure}[h]
  \centering
  \begin{tikzpicture}[very thick, scale=0.3]
  \node (h1) at (4,0){$\bullet$};
  \node (h2) at (4,2){$\bullet$};
  \node (h3) at (2,4){$\bullet$};
  \node (h4) at (0,6){$\bullet$};
  \node (h5) at (4,6){$\bullet$};
  \node (h6) at (6,4){$\bullet$};
  \draw (h1) -- (h2) ;
  \draw (h2) -- (h3) ;
  \draw (h2) -- (h6);
  \draw (h3) -- (h4) ;
  \draw (h3) -- (h5) ;

\node (hn1) at (14,0){$\bullet$};
\node (hn2) at (12,2) {$\bullet$};
\node (hn3) at (12,4) {$\bullet$};
\node (hn4) at (10,6){$\bullet$};
  \node (hn5) at (12,6){$\bullet$};
  \draw (hn1) -- (hn2) ;
  \draw (hn2) -- (hn3) ;
  \draw (hn3) -- (hn4) ;
  \draw (hn3) -- (hn5) ;
\node (hn2b) at (14,2) {$\bullet$};
\node (hn3b) at (14,4) {$\bullet$};
\node (hn4b) at (13.4,6){$\bullet$};
  \node (hn5b) at (15,6){$\bullet$};
  \draw (hn1) -- (hn2b) ;
  \draw (hn2b) -- (hn3b) ;
  \draw (hn3b) -- (hn4b) ;
  \draw (hn3b) -- (hn5b) ;
  \node (hn2c) at (16,2) {$\bullet$};
\node (hn3c) at (16,4) {$\bullet$};
\node (hn4c) at (17,6){$\bullet$};
  \node (hn5c) at (18.5,6){$\bullet$};
  \draw (hn1) -- (hn2c) ;
  \draw (hn2c) -- (hn3c) ;
  \draw (hn3c) -- (hn4c) ;
  \draw (hn3c) -- (hn5c) ;
\end{tikzpicture}

  \caption{Two successive states of a hydra in a battle}
  \label{fig:round}
\end{figure}

>>>>

\usepackage{doc}
\usepackage{tikz}
\usepackage{tikzsymbols}
\usepackage{pifont}
\newtheorem{theorem}{Theorem}
\usetikzlibrary{arrows}

@@

\institute{
Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France \\
  \email{pierre.casteran@labri.fr}
\and
to fill!
\and
to fill!
\and
MIT CSAIL, Cambridge, Massachusetts, USA
\and
to fill!
 }

@@

\begin{figure}[h]
  \centering
  \begin{tikzpicture}[very thick, scale=0.3]
  \node (h1) at (4,0){$\bullet$};
  \node[blue] (h2) at (4,2){$\bullet$};
  \node[blue] (h3) at (2,4){$\bullet$};
  \node[blue] (h4) at (0,6){$\bullet$};
  \node[blue] (h5) at (4,6){$\bullet$};
  \node[red!90!black] (h6) at (6,4){$\bullet$};
  \draw (h1) -- (h2) ;
  \draw (h2) -- (h3) ;
  \draw (h2) -- node[red!90!black,font=\small,sloped,shift={(0.01,-0.075)},rotate=90]{\textbf{\ding{34}}} (h6);
  \draw (h3) -- (h4) ;
  \draw (h3) -- (h5) ;

\node (hn1) at (14,0){$\bullet$};
\node[blue] (hn2) at (12,2) {$\bullet$};
\node[blue] (hn3) at (12,4) {$\bullet$};
\node[blue] (hn4) at (10,6){$\bullet$};
  \node[blue] (hn5) at (12,6){$\bullet$};
  \draw (hn1) -- (hn2) ;
  \draw (hn2) -- (hn3) ;
  \draw (hn3) -- (hn4) ;
  \draw (hn3) -- (hn5) ;
\node (hn2b) at (14,2) {$\bullet$};
\node (hn3b) at (14,4) {$\bullet$};
\node (hn4b) at (13.4,6){$\bullet$};
  \node (hn5b) at (14.6,6){$\bullet$};
  \draw (hn1) -- (hn2b) ;
  \draw (hn2b) -- (hn3b) ;
  \draw (hn3b) -- (hn4b) ;
  \draw (hn3b) -- (hn5b) ;
  \node (hn2c) at (16,2) {$\bullet$};
\node (hn3c) at (16,4) {$\bullet$};
\node (hn4c) at (16,6){$\bullet$};
  \node (hn5c) at (18,6){$\bullet$};
  \draw (hn1) -- (hn2c) ;
  \draw (hn2c) -- (hn3c) ;
  \draw (hn3c) -- (hn4c) ;
  \draw (hn3c) -- (hn5c) ;
\end{tikzpicture}

  \caption{Two successive states of a hydra in a battle.  Hercules chopped off the rightmost head of the hydra (red), and the whole left tree except the root node (blue) was copied twice.}
  \label{fig:round}
\end{figure}
